### 2009-07-10 docs/architecture/architecture.tex
more about data

MAESTRO's gridding is handled by the boxlib library.  The underlying
idea in boxlib is to allow for adaptive mesh refinement---different
regions of the domain can have different spatial resolutions.  The
domain is broken into boxes.  At the coarsest (base) level of
refinement, the entire computational domain is covered, either by one
box or broken across many boxes.  Higher levels of refinement have
finer zones (typically $2\times$).  Only a portion of the domain may
be covered by the higher levels of refinement.  \MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

@@

\subsection{`{\tt s}' and `{\tt u}' \multifab s}

\subsection{\tt umac}

>>>>

MAESTRO's gridding is handled by the boxlib library.  The underlying
idea in boxlib is to allow for adaptive mesh refinement (AMR)---different
regions of the domain can have different spatial resolutions.  The
domain is broken into boxes.  At the coarsest (base) level of
refinement, the entire computational domain is covered, either by one
box or broken across many boxes.  Higher levels of refinement have
finer zones (typically $2\times$).  Only a portion of the domain may
be covered by the higher levels of refinement.  \MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

@@

\subsection{`{\tt s}' and `{\tt u}' \multifab s (fluid state and velocity)}

The fluid state (density, enthalpy, species) are stored together in a
multi-component \multifab, typically named {\tt sold}, {\tt s1}, {\tt
s2}, or {\tt snew} (depending on which time-level it represents).

\subsection{{\tt umac} (the MAC velocity)}

In creating the advective fluxes, we need the velocity through the
faces of the zone---the $x$-velocity on the $x$-edges, the
$y$-velocity on the $y$-edges, etc (see figure~\ref{fig:mac}.  This
type of velocity discretization is termed the MAC velocity (after the
``marker-and-cell'' method for free boundaries in incompressible
flows, Harlow and Welch 1965).

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{\archfigpath/mac2}
\hspace{0.1in}
\begin{minipage}[b]{3.8in}
\caption{\label{fig:mac} The MAC grid for the velocity.  
Here the $x$-velocity is on the $x$-edges (shown as the 
blue points) and the $y$-velocity is on the $y$-edges
(shown as the red points).
}\ \\
\end{minipage}
\end{figure}

At each level of refinement, this is done by making a \multifab\
array where each of the {\tt dm} components is nodal in
its respective direction:
\begin{verbatim}
  type(multifab) :: umac(dm)

  do comp=1,dm
     call multifab_build(umac(n,comp), mla%la(n),1,1, &
                         nodal=edge_nodal_flag(comp,:))
  enddo
\end{verbatim}
